### 2019-11-07 paper/paper.tex
Asymmetric Residuals
Added brief discussion in new discussion section

>>>>

\section{Discussion} \label{sec:discussion}

Due to the dispersion intrinsic to echelle spectrographs, the wavelength change between pixels is greater at greater wavelengths.  This means that the function of wavelength given pixel across an order will necessarily be concave down everywhere.  Consequently, linear interpolation of this function will systematically give erroneously low values.
